New orbits for irregular satellites based on thousands of new observations and predictions of stellar occultations up to 2020

### 2016-05-23 Irregular-occ/Irregular-occ.tex
.

The initial osculating elements at the origin of integration are presented in Table \ref{Tab: sat_ell}.

@@

We compared our ephemeris to the JPL for all the Jupiter satellites we fitted, until 2018. For instance, the divergence between 2015 and 2018 is at most 98 mas in $\Delta \alpha \cos \delta$ and 58 mas in $\Delta \delta$ for Himalia and 181 mas in $\Delta \alpha \cos \delta$ and 152 mas in $\Delta \delta$ for Carme.

Fig. \ref{Fig: JPL-STE} displays the offsets of the positions published by \cite{GomesJunior2015} for the satellite Carme in declination relative to our ephemeris, to \cite{Jacobson2012} JUP300 JPL ephemeris and \cite{Emelyanov2008} ephemeris.We see that the systematic JPL ephemeris offsets pointed out by \cite{GomesJunior2015} are reduced with our ephemeris, as expected.

@@

The obtained ephemeris is hereafter refered as STE, for special-tailored ephemeris.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=8.8cm]{figures/Phoebe.eps} 
\caption{Comparison between the PH15, SAT375 JPL and \protect\cite{Emelyanov2007} ephemeris for the satellite Phoebe.}
\label{Fig:eph-Phoebe}
\end{centering}
\end{figure}

>>>>

The obtained ephemeris is hereafter refered as STE, for special-tailored ephemeris. The initial osculating elements at the origin of integration are presented in Table \ref{Tab: sat_ell}.

@@

We compared the STE ephemeris to the JPL for all the Jupiter satellites we fitted, until 2021. For instance, the divergence between 2015 and 2021 is at most 98 mas in $\Delta \alpha \cos \delta$ and 58 mas in $\Delta \delta$ for Himalia and 181 mas in $\Delta \alpha \cos \delta$ and 152 mas in $\Delta \delta$ for Carme.

Fig. \ref{Fig: JPL-STE} displays the offsets of the positions published by \cite{GomesJunior2015} for the satellite Carme in declination relative to the STE ephemeris, to \cite{Jacobson2012} JUP300 JPL ephemeris and \cite{Emelyanov2008} ephemeris.We see that the systematic JPL ephemeris offsets pointed out by \cite{GomesJunior2015} are reduced with our ephemeris, as expected.

@@

Table \ref{Tab:STE-error}

\begin{table}
\caption{\label{Tab:STE-error} Mean offsets of the \protect\cite{GomesJunior2015} positions relative to the STE, \protect\cite{Jacobson2012} and \protect\cite{Emelyanov2008} ephemeris .}
\begin{centering}
\begin{tabular}{lcccccc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
 & \multicolumn{2}{c}{STE} & \multicolumn{2}{c}{JPL} & \multicolumn{2}{c}{Eme2008}\tabularnewline
Satellite  & RA & DEC & RA & DEC & RA & DEC \tabularnewline
\hline
Ananke & 12 & 16 & 49 & 359 & 187 & 623 \tabularnewline
Carme & 20 & 14 & 30 & 369 & 220 & 653 \tabularnewline
Elara & 14 & 16 & 33 & 305 & 193 & 561 \tabularnewline
Himalia & 15 & 12 & 54 & 257 & 230 & 568 \tabularnewline
Leda & 8 & 24 & 38 & 362 & 208 & 640 \tabularnewline
Lysithea & 16 & 11 & 35 & 330 & 212 & 604 \tabularnewline
Pasiphae & 20 & 19 & 44 & 362 & 206 & 651 \tabularnewline
Sinope & 15 & 21 & 34 & 356 & 256 & 682 \tabularnewline
\hline
\end{tabular}
\par \end{centering}
\end{table}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=8.8cm]{figures/Phoebe.eps} 
\caption{Comparison between the PH15 and SAT375 JPL ephemeris for the satellite Phoebe.}
\label{Fig:eph-Phoebe}
\end{centering}
\end{figure}
